---
title: "Roborev Review Summary"
date: "`r Sys.Date()`"
format:
  html:
    page-layout: full
    embed-resources: true
    toc: true
    toc-depth: 2
    theme: darkly
    css: |
      body { background-color: #1a1a1a !important; color: #e0e0e0 !important; }
      .card { background-color: #222 !important; border-color: #444 !important; }
      table.dataTable th, table.dataTable td { background-color: #222 !important; color: #e0e0e0 !important; }
      table.dataTable thead th { background-color: #2a2a2a !important; }
      .dataTables_wrapper .dataTables_filter input { background-color: #333; color: #e0e0e0; }
      .dataTables_wrapper .dataTables_info, .dataTables_wrapper .dataTables_paginate { color: #ccc !important; }
      h2, h3 { color: #4ea8de !important; }
      .pulse-table td, .pulse-table th { padding: 4px 10px; }
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
# Load llmtelemetry: installed in CI via local::., loaded from source in dev.
# here::here() resolves to the package root regardless of render cwd.
if (!requireNamespace("llmtelemetry", quietly = TRUE)) {
  pkg_root <- tryCatch(here::here(), error = function(e) dirname(getwd()))
  if (requireNamespace("pkgload", quietly = TRUE) && file.exists(file.path(pkg_root, "DESCRIPTION"))) {
    pkgload::load_all(pkg_root, quiet = TRUE)
  } else {
    stop("llmtelemetry is not installed and pkgload::load_all() is not available. ",
         "Install the package or run devtools::load_all() first.")
  }
} else {
  library(llmtelemetry)
}
library(DT)
library(plotly)

# safe_tar_read: reads a named RDS from inst/extdata/vignettes/ if it exists,
# otherwise falls back to the fixture generator for local development.
# In CI the targets pipeline writes RDS files to inst/extdata/vignettes/
# before the vignette is rendered.
safe_tar_read <- function(name, fixture_fn = NULL) {
  rds_path <- system.file(
    file.path("extdata", "vignettes", paste0(name, ".rds")),
    package = "llmtelemetry"
  )
  if (nchar(rds_path) > 0 && file.exists(rds_path)) {
    return(readRDS(rds_path))
  }
  # Fallback: use fixture generator if provided
  if (!is.null(fixture_fn)) {
    return(fixture_fn())
  }
  stop(paste0("Target '", name, "' not found. ",
              "Run tar_make() or provide a fixture_fn."))
}

# Load fixture helpers for local development
fixture_path <- system.file(
  "testthat/fixtures/roborev_page_fixture.R",
  package = "llmtelemetry"
)
if (nchar(fixture_path) == 0) {
  # Running from source
  fixture_path <- file.path(
    here::here(), "tests", "testthat", "fixtures", "roborev_page_fixture.R"
  )
}
if (file.exists(fixture_path)) source(fixture_path)

# Load pre-computed targets (falls back to fixtures in dev)
vig_roborev_pulse <- safe_tar_read(
  "vig_roborev_pulse",
  fixture_fn = if (exists("make_roborev_findings")) function() {
    build_pulse_table(make_roborev_findings(), make_roborev_loops())
  } else NULL
)

vig_roborev_trend <- safe_tar_read(
  "vig_roborev_trend",
  fixture_fn = if (exists("make_roborev_findings")) function() {
    plot_open_findings_trend(make_roborev_findings())
  } else NULL
)

vig_roborev_top <- safe_tar_read(
  "vig_roborev_top",
  fixture_fn = if (exists("make_roborev_findings")) function() {
    plot_top_files(make_roborev_findings())
  } else NULL
)

vig_roborev_loops <- safe_tar_read(
  "vig_roborev_loops",
  fixture_fn = if (exists("make_roborev_loops")) function() {
    plot_loops_table(make_roborev_loops())
  } else NULL
)

vig_roborev_inflow <- safe_tar_read(
  "vig_roborev_inflow",
  fixture_fn = if (exists("make_roborev_findings")) function() {
    plot_inflow_outflow(make_roborev_findings())
  } else NULL
)

vig_roborev_resolution <- safe_tar_read(
  "vig_roborev_resolution",
  fixture_fn = if (exists("make_roborev_findings")) function() {
    plot_resolution_time(make_roborev_findings())
  } else NULL
)

vig_roborev_recent <- safe_tar_read(
  "vig_roborev_recent",
  fixture_fn = if (exists("make_roborev_findings")) function() {
    build_recent_table(make_roborev_findings(), days = 30L)
  } else NULL
)

# Convenience helpers for inline prose
n_open <- if (is.data.frame(vig_roborev_pulse)) {
  row <- vig_roborev_pulse[vig_roborev_pulse$metric == "Open findings", ]
  if (nrow(row) > 0) row$value[1] else "—"
} else "—"

n_loops <- if (is.data.frame(vig_roborev_pulse)) {
  row <- vig_roborev_pulse[vig_roborev_pulse$metric == "Active loops", ]
  if (nrow(row) > 0) row$value[1] else "—"
} else "—"

n_escalate <- if (is.data.frame(vig_roborev_pulse)) {
  row <- vig_roborev_pulse[vig_roborev_pulse$metric == "  Escalate (no ack)", ]
  if (nrow(row) > 0) row$value[1] else "—"
} else "—"
```

[roborev (the automated code-review system)](https://github.com/JohnGavin/llm/issues/144)
is the project's hook-driven review pipeline that runs `critic` and `fixer` agents on
every commit and tracks whether findings recur across review rounds. This page provides
a single-glance health summary of the review pipeline's current state.

## 1. Pulse

Current state at a glance. All values are computed from the pre-built targets pipeline
and reflect the latest `tar_make()` run. There are currently **`r n_open`** open
findings and **`r n_loops`** active
<a href="https://github.com/JohnGavin/llm/issues/144"><abbr title="roborev: automated code-review system that tracks findings across review rounds">roborev</abbr></a>
loops, of which **`r n_escalate`** are in the Tier 3 escalate state with no acknowledgement.

```{r pulse-table}
if (is.data.frame(vig_roborev_pulse) && nrow(vig_roborev_pulse) > 0) {
  knitr::kable(
    vig_roborev_pulse,
    col.names = c("Metric", "Value"),
    format = "html",
    table.attr = 'class="table table-sm table-dark pulse-table"'
  )
}
```

## 2. Trends

Open finding counts over time, broken down by severity. The stacked area chart
shows how the backlog has evolved — widening bands indicate accumulation, shrinking
bands indicate resolution progress. The range slider defaults to the last 90 days;
drag to inspect older periods.

```{r trend-plot}
if (!is.null(vig_roborev_trend)) vig_roborev_trend
```

Weekly inflow (new findings opened) versus outflow (findings resolved) shows the
velocity balance. When inflow consistently exceeds outflow the backlog grows; the
goal is net-zero or negative weeks. The line chart uses the same severity palette
as the trend above, with range slider defaulting to the last 90 days.

```{r inflow-outflow}
if (!is.null(vig_roborev_inflow)) vig_roborev_inflow
```

Median hours to resolve a finding, by severity. Critical findings that take hundreds
of hours to resolve indicate blocked escalation paths; low findings with long
resolution times may indicate deprioritisation. Points are coloured using the same
severity palette as all other charts on this page.

```{r resolution-time}
if (!is.null(vig_roborev_resolution)) vig_roborev_resolution
```

## 3. Top Problems

Files ranked by open-finding count. The Cleveland dot plot shows each file as a point
at its open count, coloured by the most severe open finding. Files near the right edge
of the chart are highest-priority review targets — they have accumulated the most
unresolved findings. Only the top 15 files are shown; hover a point to see counts and
worst severity.

```{r top-files}
if (!is.null(vig_roborev_top)) vig_roborev_top
```

## 4. Loop Detector

A "loop" is a finding that has been flagged, fixed, and re-opened more than once
across multiple review cycles. Loops indicate that the fix did not address the root
cause, or that a systemic pattern keeps re-introducing the same defect.

The table below lists all detected loops, sorted by cycle count (most repetitions
first). Row colour encodes the loop tier:

- **Escalate** (red): stuck loops with no acknowledgement — Tier 3 escalation issues
  are filed automatically via `inst/scripts/escalate_stuck_loops.R`.
- **Block** (orange): loops actively blocking review resolution.
- **Watch** (yellow): loops under monitoring but not yet blocking.

```{r loops-table}
if (!is.null(vig_roborev_loops)) vig_roborev_loops
```

## 5. Recent Activity

All findings opened or resolved in the last 30 days, ordered by find date descending.
Use the search box to filter by file, severity, or summary text.

```{r recent-activity}
if (!is.null(vig_roborev_recent)) vig_roborev_recent
```

## Methodology

### What this vignette computes

This vignette displays the current state of the
<a href="https://github.com/JohnGavin/llm/issues/144"><abbr title="roborev: automated code-review system that tracks findings across review rounds">roborev</abbr></a>
review pipeline. It reads seven pre-computed targets — `vig_roborev_pulse`,
`vig_roborev_trend`, `vig_roborev_top`, `vig_roborev_loops`, `vig_roborev_inflow`,
`vig_roborev_resolution`, and `vig_roborev_recent` — built by
`plan_roborev_vignette()` from the `roborev_findings` and `roborev_loops` upstream
targets. Zero inline computation is performed in this vignette: all aggregations
and chart objects are produced by the pipeline and served as RDS files from
`inst/extdata/vignettes/` in CI.

### Data sources

- `roborev_findings` target: produced by Agent 1's `plan_roborev.R`; sourced from
  the `roborev_findings` table in `~/.claude/logs/unified.duckdb`, refreshed on
  every `critic` + `fixer` agent run.
- `roborev_loops` target: produced by Agent 2's loop-detection plan; written to
  `~/.claude/logs/unified.duckdb` by the `detect_loops()` function run after each
  review cycle.
- During local development and testing: `tests/testthat/fixtures/roborev_page_fixture.R`
  provides synthetic data with the same shape as production.

### AI disclosure

This vignette was developed with assistance from Anthropic's Claude (model: Opus 4.7
and Sonnet 4.6). AI helped with code structure, prose drafting, and visualization
choices. All analytical decisions and data interpretations are the author's
responsibility.
