---
title: "Self-Review Findings"
date: "`r Sys.Date()`"
format:
  html:
    page-layout: full
    embed-resources: true
    toc: true
    toc-depth: 2
    theme: darkly
    css: |
      body { background-color: #1a1a1a !important; color: #e0e0e0 !important; }
      .card { background-color: #222 !important; border-color: #444 !important; }
      table.dataTable th, table.dataTable td { background-color: #222 !important; color: #e0e0e0 !important; }
      table.dataTable thead th { background-color: #2a2a2a !important; }
      .dataTables_wrapper .dataTables_filter input { background-color: #333; color: #e0e0e0; }
      .dataTables_wrapper .dataTables_info, .dataTables_wrapper .dataTables_paginate { color: #ccc !important; }
      h2, h3 { color: #4ea8de !important; }
      .metric-table td, .metric-table th { padding: 4px 10px; }
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| label: setup

library(jsonlite)
library(dplyr, warn.conflicts = FALSE)
library(plotly)
library(DT)

# Palette — single source of truth for this page (narrative-colour-persistence)
PALETTE <- c(
  "stuck_loop"           = "#f08080",
  "high_tool_error_rate" = "#ffd93d",
  "critical"             = "#f08080",
  "major"                = "#ffd93d",
  "minor"                = "#69d4a0"
)

# Load the committed JSON snapshot (works in CI without the live DB)
sr_path <- {
  # Try installed package path
  p <- system.file("extdata", "self_review_findings.json", package = "llmtelemetry")
  if (!nzchar(p) || !file.exists(p)) {
    p <- file.path(here::here(), "inst", "extdata", "self_review_findings.json")
  }
  p
}

sr_df <- if (file.exists(sr_path)) {
  tryCatch(
    jsonlite::fromJSON(sr_path, simplifyDataFrame = TRUE),
    error = function(e) data.frame()
  )
} else {
  data.frame()
}

# Ensure correct types
if (is.data.frame(sr_df) && nrow(sr_df) > 0) {
  sr_df$date <- as.Date(sr_df$date)
} else {
  sr_df <- data.frame(
    finding_id       = character(0),
    finding_type     = character(0),
    severity         = character(0),
    date             = as.Date(character(0)),
    evidence_summary = character(0),
    stringsAsFactors = FALSE
  )
}

# Convenience scalars for dynamic prose (dynamic-prose-values rule)
n_total    <- nrow(sr_df)
n_by_type  <- if (n_total > 0) table(sr_df$finding_type) else table(character(0))
n_loops    <- as.integer(n_by_type["stuck_loop"] %||% 0L)
n_errors   <- as.integer(n_by_type["high_tool_error_rate"] %||% 0L)
date_min   <- if (n_total > 0) format(min(sr_df$date, na.rm = TRUE), "%Y-%m-%d") else "—"
date_max   <- if (n_total > 0) format(max(sr_df$date, na.rm = TRUE), "%Y-%m-%d") else "—"
```

The self-review dashboard tracks operational health findings produced by the automated session monitoring in `~/.claude/logs/unified.duckdb`. There are currently **`r n_total`** total findings from `r date_min` to `r date_max`: **`r n_loops`** stuck-loop findings and **`r n_errors`** high tool-error-rate findings.

## 1. Pulse

Summary counts across finding types and severity levels, derived from the live snapshot.

```{r pulse-table}
#| label: pulse-table

if (n_total > 0) {
  pulse <- sr_df |>
    count(finding_type, severity) |>
    arrange(desc(n))
  knitr::kable(
    pulse,
    col.names = c("Finding Type", "Severity", "Count"),
    format = "html",
    table.attr = 'class="table table-sm table-dark metric-table"'
  )
} else {
  cat("No findings recorded yet.")
}
```

## 2. Trend Over Time

Daily count of new findings by type. Widening bars indicate the monitor is surfacing more issues; the goal is a flat or declining pattern once systemic problems are resolved. The range slider defaults to the full available window.

```{r trend-plot}
#| label: trend-plot
#| fig-alt: "Daily count of self-review findings by finding type, plotted as a stacked bar chart. Stuck-loop findings (red) and high-tool-error-rate findings (yellow) are shown from 2026-05-25 onwards. The chart includes a range slider."

if (n_total > 0) {
  daily_counts <- sr_df |>
    count(date, finding_type) |>
    arrange(date)

  plot_ly(
    daily_counts,
    x      = ~date,
    y      = ~n,
    color  = ~finding_type,
    colors = PALETTE[unique(daily_counts$finding_type)],
    type   = "bar",
    text   = ~paste0(finding_type, ": ", n),
    hoverinfo = "x+text"
  ) |>
    layout(
      barmode  = "stack",
      title    = list(text = "Daily Self-Review Findings by Type", font = list(color = "#e0e0e0")),
      xaxis    = list(
        title       = "Date",
        color       = "#e0e0e0",
        gridcolor   = "#333",
        rangeslider = list(visible = TRUE)
      ),
      yaxis    = list(title = "Count", color = "#e0e0e0", gridcolor = "#333"),
      paper_bgcolor = "#1a1a1a",
      plot_bgcolor  = "#1a1a1a",
      legend        = list(font = list(color = "#e0e0e0")),
      font          = list(color = "#e0e0e0")
    )
} else {
  cat("No findings to plot.")
}
```

## 3. Findings by Type

Breakdown of finding counts by type. Stuck loops are sessions where an agent repeated
the same pattern more than a configured threshold number of times; high tool-error-rate
findings flag sessions where a specific tool failed repeatedly.

```{r type-plot}
#| label: type-plot
#| fig-alt: "Cleveland dot plot showing total finding count by finding type. Stuck-loop findings appear in red and high-tool-error-rate findings in yellow."

if (n_total > 0) {
  type_counts <- sr_df |>
    count(finding_type) |>
    arrange(n) |>
    mutate(finding_type = factor(finding_type, levels = finding_type))

  plot_ly(
    type_counts,
    x      = ~n,
    y      = ~finding_type,
    type   = "scatter",
    mode   = "markers",
    marker = list(
      size  = 14,
      color = PALETTE[as.character(type_counts$finding_type)]
    ),
    text      = ~paste0(finding_type, ": ", n),
    hoverinfo = "text"
  ) |>
    layout(
      title  = list(text = "Total Findings by Type", font = list(color = "#e0e0e0")),
      xaxis  = list(title = "Count", color = "#e0e0e0", gridcolor = "#333", zeroline = FALSE),
      yaxis  = list(title = "", color = "#e0e0e0", gridcolor = "#333"),
      paper_bgcolor = "#1a1a1a",
      plot_bgcolor  = "#1a1a1a",
      font          = list(color = "#e0e0e0")
    )
} else {
  cat("No findings to plot.")
}
```

## 4. All Findings Table

All `r n_total` findings with their evidence summaries. Use the search box to filter by date, type, or any evidence field.

```{r findings-table}
#| label: findings-table

if (n_total > 0) {
  tbl_data <- sr_df |>
    select(date, finding_type, severity, evidence_summary) |>
    arrange(desc(date))

  DT::datatable(
    tbl_data,
    caption  = paste0(
      "Self-review findings from ", date_min, " to ", date_max,
      ". Source: self_review_findings_stage1 in ~/.claude/logs/unified.duckdb."
    ),
    colnames = c("Date", "Finding Type", "Severity", "Evidence"),
    rownames = FALSE,
    filter   = "top",
    options  = list(
      pageLength = 15,
      dom        = "ftip",
      scrollX    = TRUE
    ),
    class = "table table-dark table-sm"
  )
} else {
  cat("No findings recorded yet.")
}
```

## Methodology

### What this vignette computes

This vignette displays the current state of the self-review monitoring pipeline.
It reads the sanitised findings snapshot from `inst/extdata/self_review_findings.json`,
produced from the `self_review_findings_stage1` table in `~/.claude/logs/unified.duckdb`
by `inst/scripts/export_dashboard_data.R` (section 8z). The snapshot contains
`r n_total` rows spanning `r date_min` to `r date_max`, with one row per finding.
Four visualisations are shown: pulse summary table, daily trend bar chart,
type breakdown dot plot, and full findings table.

### Data sources

- `inst/extdata/self_review_findings.json`: sanitised export of
  `self_review_findings_stage1` from `~/.claude/logs/unified.duckdb`.
  Columns: `finding_id` (opaque hash), `finding_type`, `severity`, `date`
  (YYYY-MM-DD, from `detected_at`), `evidence_summary` (JSON string with safe
  operational fields only — no session IDs or filesystem paths).
  Written locally by `export_dashboard_data.R` section 8z; copied to
  `vignettes/data/` for CI serving.
- Linked issue: [llmtelemetry#207](https://github.com/JohnGavin/llmtelemetry/issues/207)
  and [llm#235](https://github.com/JohnGavin/llm/issues/235) (schema origin).

### AI disclosure

This vignette was developed with assistance from Anthropic's Claude (model: Opus 4.7
and Sonnet 4.6). AI helped with code structure, prose drafting, and visualization
choices. All analytical decisions and data interpretations are the author's
responsibility.
